MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-07-26 darmstadt_gscl_2013/article_twitter_normalization.tex
bibliography dir added, a few lines updated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{paralist} % for inparaenum
\usepackage{multirow} % for multirow
\usepackage{tabularx} % for centering in table
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\totaloov}{\% of total OOVs}
\newcommand{\uniqoov}{\% of unique OOVs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{headings}  % switches on printing of running heads
\title{MT @HanBaldwin: Fightin OOVs in German \#twitter}
\titlerunning{Makn Sens a Germa \#twitter}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Max Mustermann \and Otto Normalverbraucher \and John Doe}
%
\authorrunning{xxx et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Max Mustermann, Otto Normalverbraucher, John Doe}
%
\institute{University of Universe, Milky Way City,\\
  \email{max@example.com, %
    otto@example.com, %
    john@example.com},\\
  WWW home page: \texttt{http://www.example.com}}

@@

  This article gives an overview of existing approaches to the
  problems of out-of-vocabulary tokens and noisiness effects in
  natural language texts. Additionally, quantitative and qualitative
  analyses of unknown words in German tweets are conducted in order to
  assess how widely this textual genre differs from standard language
  texts with regard to noisiness phenomena. Subsequently, we present a
  set of ad-hoc techniques which are supposed to tackle some of the
  most prominent disturbing effects and show how this set of
  techniques allows us to lower the average rate of out-of-vocabulary
  tokens in Twitter messages.

@@

Though the problem of out-of-vocabulary (OOV) words and its related
task of text normalization have been extensively studied in
computational linguistics since as early as the late 1950s
(cf. Petersen, \cite{petersen}) and were certainly anything but new at
the time when mobile communication emerged, it were small messages
that revived interest in this area in the past two decades.

@@

In the next Section we will give a short overview of recent scientific
approaches to the problem of tackling out-of-vocabulary words in
non-standard texts. After that, in Section \ref{error:analysis} we
will analyze which types of text noisiness phenomena are especially
characteristic for German Twitter. Section \ref{normalization} will
subsequently describe an automatic procedure for mitigating some of
the most obvious of those effects. In a concluding step, we will
perform an evaluation of the results of this procedure and give
further suggestions for future research.

@@

Before proceeding with the description of existing methods for noisy
text normalization (NTN) task, we first would like to define the
criteria by which these methods could be classified. It should be
noted that there already exist several classifications of NTN methods
including, for example, Kukich (\cite{kukich}), Kobus et
al. (\cite{kobus}), and Sproat et al. (\cite{sproat}). But all of
these classification attempts seem to have one significant
shortcoming, namely they try to involve several independent criteria
within one classification scheme.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{paralist} % for inparaenum
\usepackage{multirow} % for multirow
\usepackage{tabularx} % for centering in table
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\totaloov}{\% of total OOVs}
\newcommand{\uniqoov}{\% of unique OOVs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{headings}  % switches on printing of running heads
\title{MT @HanBaldwin: Fightin OOVs in German \#twitter}
\titlerunning{Makn Sens a Germa \#twitter}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Uladzimir Sidarenka \and Tatjana Schef\/f\/ler \and Manfred Stede}
%
\authorrunning{Sidarenka et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Uladzimir Sidarenka, Tatjana Schef\/f\/ler, Manfred Stede}
%
\institute{University of Potsdam,\\
  \email{{uladzimir.sidarenka@uni-potsdam.de,
      tatjana.scheffler@uni-potsdam.de,
      manfred.stede@uni-potsdam.de},\\ WWW home page:
    \texttt{http://www.ling.uni-potsdam.de/acl-lab/SocMedia/main.htm}}}

@@

  This article gives an overview of existing approaches to the problem
  of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
  language texts. These approaches are classified with regard to the
  size of text spans and knowledge inference mechanisms which they use
  in their work. Subsequently, quantitative and qualitative analyses
  of unknown words are conducted on German Twitter messages, in order
  to see how relevant the OOV issue is for this particular kind of
  micro-texts and to determine which peculiarities are especially
  characteristic for them. In a concluding step, we present a set of
  ad-hoc techniques which are supposed to tackle some of the most
  prominent disturbing effects found during the analyses and show how
  this set of techniques helps us to lower the average rate of
  out-of-vocabulary tokens in Twitter messages thereby improving their
  automatic Part-of-speech tagging quality.

@@

Though the problem of out-of-vocabulary (OOV) words and its closely
related task of textual normalization have been extensively studied in
computational linguistics since as early as the late 1950s
(cf. Petersen, \cite{petersen}) and were certainly anything but new at
the time when mobile communication emerged, it were small messages
that revived interest in this research area in the past two
decades.

Starting from the second half of 1990-ies, the rise of SMS messages,
growing popularity of online chats and launch of social networks lead
to a significant boost in the number of publications on preprocessing
casually typed texts. But despite this increased number of researches,
the main focus of the majority of these works was on English data with
a few exceptions of works on Spanish (Oliva et al., \cite{oliva}) and
French (Beaufort et al., \cite{beaufort}).

@@

In the next Section we will give a short overview of recent scientific
approaches to the problem of out-of-vocabulary words in non-standard
texts. After that, in Section \ref{error:analysis} we will analyze
which types of noisiness phenomena are especially characteristic for
German Twitter. Section \ref{normalization} will subsequently describe
an automatic procedure for mitigating some of the most obvious of
those effects. In a concluding step, we will perform an evaluation of
the results of this procedure and give further suggestions for future
research.

@@

Before proceeding with the description of existing methods for noisy
text normalization (NTN), we first would like to define the criteria
by which these methods could be classified. It should be noted that
there already exist several classifications of NTN methods including,
for example, Kukich (\cite{kukich}), Kobus et al. (\cite{kobus}), and
Sproat et al. (\cite{sproat}). But all of these classification
attempts seem to have one common shortcoming, namely they try to
involve several independent criteria within one classification scheme.

@@

\bibitem[2012]{mukherjee}
  Mukherjee, S., Malu, A., Balamurali, A. R., Bhattacharyya, P.: %
  TwiSent: A Multistage System for Analyzing Sentiment in Twitter. %
  In Proceedings of The 21st ACM Conference on Information and %
  Knowledge Management CIKM 2012, Hawai, (Oct 29 - Nov 2, 2012)

  McVeigh, T.: %
  Text messaging turns 20. %
  The Observer (December 1, 2012)
